Effects of CHILDREN's programs

### 2020-02-26 paper.Rnw

\begin{figure}
  \caption{Health outcome over time}
  \label{Health_timeplots}
<<Health time plots, echo=FALSE, message=FALSE>>=
Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
print(Health_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

@@

In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise. Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Equality of opportunities over time}
  \label{Equality_timeplots}
<<Equality time plots, echo=FALSE, message=FALSE>>=
Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
print(Equality_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).  
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
\end{figure}

@@

In this section we use a simple linear model with, as described in equation \ref{SimpleLinear Model}. We look at the association between:

@@

texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')
@

>>>>

\begin{figure}
  \caption{Health outcome over time}
  \label{Health_timeplots}
<<HealthTimePlots, echo=FALSE, message=FALSE>>=
Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
print(Health_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

@@

In its yearly surveys, CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise. Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Equality of opportunities over time}
  \label{Equality_timeplots}
<<EqualityTimePlots, echo=FALSE, message=FALSE>>=
Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
print(Equality_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).  
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
\end{figure}

@@

In this section we use a simple linear model, as described in equation \ref{SimpleLinear Model}. We look at the association between:

@@

texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')

@
